%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Bilegjargal Jargalsaikhan "Jargal"}
   & Email : \href{mailto:bjargal56@gmail.com}{bjargal56@gmail.com}\\
   & Mobile : +1-773-754-6016 \\
   & \href{https://www.linkedin.com/in/bileg-jargal/}{http://linkedin.com/in/bileg-jargal}\\
   & \href{http://bilegjargal.me}{http://bilegjargal.me}
\end{tabular*}

%--------SKILLS------------
\section{Skills}
   {
     \textbf{JavaScript: }{ES6, React.js, Redux, Node.js, Angular, Express, Cypress, Jest, npm, yarn}
   } \\
   {
     \textbf{Cloud: }{AWS-CloudFormation, Terraform, OpenSearch, EC2, ECS, OS-Ubuntu, CentOS, Docker } 
   } \\
   {
     \textbf{SQL: }{MySQL, Oracle, MongoDB, DocumentDB, SQLite}
   } \\

%-----------EXPERIENCE-----------------
\section{Experience} 
      \vfill
      \textbf{Arc XP / Arlington, VA}\hfill \textit{Software Engineer, June 2021 - Present} \\
      {
        Providing well documented, quality, clean code using technologies including React.js, TypeScript, Node.js, AWS, Java and Kafka
      }
      \resumeItemListStart
        \item{
          Collaborating on product development and design to build an ArcXP content creation platform.
        }
        \item{
          Enhanced the functionality of the internal automated testing library which is used by teams across the Arc XP
        }
        \item{
          Participating in on-call support rotation to handle real-time incidents and document root cause analysis report
        }
      \resumeItemListEnd

      \vfill
      \textbf{Grainger / Lake Forest, Illinois}\hfill \textit{Software Engineer(Contract), Mar 2020 - May 2021}
      \resumeItemListStart
        \item{
        Developed a vending machine application which requires to be working on low-performance mini PCs, using React, Redux, Express, and Electron.
        }
        \item{
        Participated in re-platforming application architecture to using cloud services(AWS, Circle-CI pipeline, Containerizing the application)
        }
        \item{
        Boosted render performance of the application speed by 160 percent by refactoring the component using memoization
        }
      \resumeItemListEnd

      \vfill
      \textbf{Hub Group / Oak Brook, Illinois}\hfill \textit{Software Engineer(Contract), Jul 2019 - Mar 2020}
      \resumeItemListStart
        \item{
          Worked on a microservice-based web application using Node.js, Express, Angular, MongoDB (MEAN stack) in the transportation domain industry.
        }
        \item{
          Developed Single Page Application using modern Javascript technologies such as Angular, Node, Express along with unit testing frameworks Chai and Jest. 
        }
        \item{
          Reduced the number of address validation API calls. As a result, the cost of third party API usage reduced by 25%
        }
        \item{
          Worked with logging tool Kibana, and Graylog for monitoring system integration durability. Also used Apache JMeter for load testing by sending multiple concurrent requests to the server.
        }
        \item{
          Worked closely with the DevOps team in creating an automatic build and deployment process using Jenkins. 
        }
      \resumeItemListEnd

      \vfill
      \textbf{ITZONE COMPANY / Ulaanbaatar, Mongolia }\hfill \textit{Software Developer, Sep 2016 - Jul 2018}
      \resumeItemListStart
        \item{
          Worked as a full-stack software developer on a business tool for contract management, using React, Redux, Node, Express, and MongoDB, contributing to all phases of the software development process, including sprint planning, development, iteration reviews, and deployment.
        }
        \item{
          Implemented a new functionality feature to add dynamic fields to a contract document. As a result, the implementation time for a new customer is reduced by 30 percent.
        }
        \item{
          Created a feature that generates a contract payment schedule by weekly, monthly, or custom time interval with automatic invoice creation.
        }
      \resumeItemListEnd
  
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Maharishi University of Management}{Fairfield, IOWA}
      {Master of Science in Computer Science;}{Aug. 2018 -- Dec, 2020}
    \resumeSubheading
      {Mongolian University of Science and Technology}{Ulaanbaatar, Mongolia}
      {Bachelor of Science in Computer Science;}{Aug. 2012 -- Jun. 2016}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
